Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2018-03-03 readme.Rmd
Add instructions for compiling SI

### Dependencies
- R (including knitr and various packages called by scripts)  
- LaTeX (optional, see below)  
- RStudio (optional, see below)
- latex2rtf (optional, see below)

@@

### Instructions
Clone or [download](https://github.com/joelnitta/canopylife/archive/master.zip) and unzip this repository, and navigate to it.

Analyses were conducted in R, and each can be run separately from `bin/`.

@@

#### - From the terminal
This method should work with a full LaTeX distribution.

@@

#### - Overleaf
This method does not require LaTeX to be installed at all.

@@

#### - RStudio
This method should work with a minimal LaTeX distribution if the packages used in the tex file are installed.

@@

#### - Tables only
To convert the pdf to MS Word for submission of the manuscript, the [copy-and-paste method](https://joelnitta.com/blog/getting-latex-into-word) was used. This works Pretty Darn Well, except for tables, which get garbled during pasting. To convert tables to MS Word (i.e., rich text) format, latex2rtf works better. However, latex2rtf is limited in the LaTeX packages it can use. A simple knitr file using only bare-bones LaTeX packages is available to output a tex file containing only tables, which can then be processed by latex2rtf. After knitting manuscript.Rnw, run the following:

```
Rscript -e "library(knitr); knit('./tables.Rnw')"
latex2rtf tables.tex
```
### Cleanup
Run this script from the terminal to remove intermediate files generated during compiling the pdf. This can't be undone, so use with care!

>>>>

### Dependencies

- R (including knitr and various packages called by scripts)  
- RStudio (optional, see below)
- LaTeX (optional, see below)  
- latex2rtf (optional, see below)

@@

### Getting started

Clone or [download](https://github.com/joelnitta/canopylife/archive/master.zip) and unzip this repository, and navigate to it.

All analyses were conducted in R, and each can be run separately from `bin/`.

### Compiling the manuscript

@@

#### - From the terminal

This method should work with a full LaTeX distribution.

@@

#### - Overleaf

This method does not require LaTeX to be installed at all.

@@

#### - RStudio

This method should work with a minimal LaTeX distribution if the packages used in the tex file are installed.

@@

### Compiling Supporting Information

After compiling the manuscript using one of the methods above and before running `cleanup.sh` (so that `results.Rdata` is still present), compile the SI in the same way but replace `manuscript` with `supporting_information`.

### Compiling tables only

To convert the pdf to MS Word for submission of the manuscript, the [copy-and-paste method](https://joelnitta.com/blog/getting-latex-into-word) was used. This works Pretty Darn Well, except for tables, which get garbled during pasting. To convert tables to MS Word (i.e., rich text) format, latex2rtf works better. However, latex2rtf is limited in the LaTeX packages it can use. A simple knitr file using only bare-bones LaTeX packages is available to output a tex file containing only tables, which can then be processed by latex2rtf.

After knitting manuscript.Rnw and before running `cleanup.sh`, run the following:

```
Rscript -e "library(knitr); knit('./tables.Rnw')"
latex tables.tex
bibtex tables.aux
latex tables.tex
latex2rtf tables.tex
```

### Cleanup

Run this script from the terminal to remove intermediate files generated during compiling the pdf. This can't be undone, so use with care!
